\input{thispreamble.tex}

\renewcommand\AUTHOR{nweadick1@cougars.ccis.edu} % CHANGE TO YOURS

\begin{document}
\topmattertwo

This is a closed-book, 5-min quiz.

%------------------------------------------------------------------------------
\nextq
There are 200 students who has taken a course in Physics,
100 who have taken a course in Chemistry,
50 who has taken a course in Physics and Chemistry.
How many students have taken either Physics or Chemistry?
Write ERROR if the problem cannot be solved.
\\
\ANSWER
\begin{answerlong}
Let P be the set of students who has taken a course in Physics.

Let C be the set of students who has taken a course in Chemistry.

Let $|P| = 200$ 

Let $|C| = 100$

Then, $|P \cup C| = 300$ and $|P \cap C| = 50$

Therefore" is about the sum of terms in the PIE formula.

$|P \cup C| - |P \cap C| = 300 - 50 = 250$

\end{answerlong}
(You only need to state the answer.)

%------------------------------------------------------------------------------
\nextq 
How many elemets are in the union of 4 sets if
each of the sets has 100 elements,
each pair of the sets shares 40 elements,
each three of the sets share 25 elements, and
there are 5 elements in all four sets?
Write ERROR if the problem cannot be solved.
\\
\ANSWER
\begin{answerlong}
Let the four sets be $A,B,C,D$

$|A \cup B \cup C \cup D| = 400$

The sum of the size of intersections of two distinct sets is therefore, $6 \cdot 40 = 240$.

The sum of the size of intersections of three distinct sets is therefore, $25 \cdot 4 = 100$.

The sum of the size of intersections of four distinct sets is therefore, $1 \cdot 5 = 5$.

Therefore" is about the sum of terms in the PIE formula,

$400 - 240 + 100 - 5 = 255$
\end{answerlong}
(You only need to state the answer.)

%------------------------------------------------------------------------------
\newpage
\input{instructions.tex}
\end{document}
