\input{thispreamble.tex}

\renewcommand\AUTHOR{nweadick1@cougars.ccis.edu} % CHANGE TO YOURS

\begin{document}
\topmattertwo

\textsc{Objectives}
\begin{enumerate}
\item Solve counting problems using principle of
inclusion-exclution.
\end{enumerate}
\vspace{1cm}



The following are practice problems for self-study:
\begin{enumerate}[nosep]
\li Rosen 8th edition, section 8.6: Odd numbered problems 1-25 except 15.
Solutions to many of the questions are included.
23 was covered in class.
Some questions (example 19, 24) are small theorems -- you are
encourage to try them and talk to me if you have questions.
\end{enumerate}
For this assignment the problems you need to solve are
\begin{enumerate}[nosep]
\li Rosen 8th edition, section 8.6: \underline{questions 4, 6, 10, 17}.
\end{enumerate}
Explain your work completely using the solutions provided as
guide and examples on how to write math properly.

In \LaTeX\, math notation is enclosed by the \verb!$! symbols.
For instance \verb!$x = a_{1} + b^{2}$! gives you $x = a_{1} + b^{2}$.
For emphasis you can write also write it as
\verb!\[ x = a_{1} + b^{2} \]!
to center your math:
\[
x = a_{1} + b^{2}
\]
For binomial coefficients, \verb!$\binom{5}{2}$! will give you 
$\binom{5}{2}$.
You can also look at the solutions, find something that you can use,
copy-and-paste, and modify.

For more information about \LaTeX\, go to my
website
\href{http://bit.ly/yliow0}{http://bit.ly/yliow0},
click on \verb!Yes!
you are one of my students,
then look for
\href{https://drive.google.com/file/d/0BzjYrK0VFuMWZm5xV0kyR3J2Zm8/view?usp=sharing}{latex.pdf}.)
Even easier: ask questions in CCCS discord.




For each question in section 8.6,
you must define your universe $U$ and
the propositional formulas $P_1, P_2, P_3$.
(Of course different problems have different numbers of
propositional formulas; you might need more or less.) 
You can use other subscripts such as $P_A, ...$
if you find it easier to read the solution that way.

After stating the above, you have to argue that the 
required number is $N(P_1' P_2' P_3')$.
In most cases, it should be obvious.
If that's the case you just say
\lq\lq The required number is clearly $N(P_1' P_2' P_3' ...)$''.
In some cases it might not be clear.
You h ave to judge for yourself.

After stating the above, you must state the version of P.I.E. you are
using. For instance you might want to say \lq\lq
By the principle of inclusion-exclusion,
\[
N(P_1' P_2' P_3') = |U| - ...
\]
Do NOT use $U$ or $P_i$'s if it's not defined.

After that you should compute the values $|U|$, $N(P_1)$, ..., $N(P_1P_2)$, ...
If the computation of $N(P_2)$ is similar to $N(P_1)$, then 
you may say \lq\lq Similarly $N(P_2) = ...$".
For easy and straightforward cases (example: the number is something from
Discrete I), you simply state the number. For instance:
\lq\lq We have $|U| = 2^5$.'' or \lq\lq Clearly $|U| = 2^5$.''
Learn to write \textit{full} sentences: 
writing \lq\lq $|U| = 2^5$'' out of nowhere
is very confusing and misleading.

Again you do not need to show trivial computations.
The general rule is this: 
If the result is from Discrete I (or previous classes), then you can use the
relevant formula right away without too much explanation.
If a result you want to use is not from previous classes,
then you need to explain how to change the computation to one
involving previous results.

Once all the quantities are stated/computated, you substitute
them into the P.I.E. that you have stated.

Finally state what you have found clearly.
For instance you might want to say \lq\lq Therefore
the number of students studying Biology and Physics is 115''.

Draw a box around your final answer if the question required
an explicit answer (i.e., if it's not a proof question).

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 1.

\SOLUTION

\input{08-06-01.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 2.

\SOLUTION

\input{08-06-02.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 3.

\SOLUTION

\input{08-06-03.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 4.

\SOLUTION
$ N = \binom{17+3}{17} = 1140$

$N(P1) = number of solutions with x1 >= 4 = \binom{16}{13} = 560$

$N(P2) = number of solutions with x2 >= 5 = \binom{15}{12} = 455$

$N(P3) = number of solutions with x3 >= 6 = \binom{14}{11} = 364$

$N(P4) = number of solutions with x4 >= 9 = \binom{11}{8} = 165$

$N(P1P2) = \binom{11}{8} = 165$

$N(P1P3) = \binom{10}{7} = 120$

$N(P1P4) = \binom{7}{4} = 35$

$N(P2P3) = \binom{9}{6} = 84$

$N(P2P4) = \binom{6}{3} = 20$

$N(P3P4) = \binom{4}{2} = 6$

$N(P1P2P3) = \binom{4}{2} = 6$

$N(P1P2P4) = 0$

$N(P2P3P4) = 0$

$N(P1P2P3P4) = 6$

$1140 - (560+455+354+165) + (165+120+35+84+20+6) - 6$

\answerbox{20}

\input{08-06-04.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 5.

\SOLUTION

\input{08-06-05.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 6.

An integer is called squarefree if it is not divisible by
the square of a positive integer greater than 1. Find the
number of squarefree positive integers less than 100.

\SOLUTION

$99$

$- (\floor{\frac{99}{2^2}} + \floor{\frac{99}{3^2}} + \floor{\frac{99}{5^2}}+  \floor{\frac{99}{7^2}})$

$+ \floor{\frac{99}{2^2 \cdot 3^2}}$

$99 - (24 + 11 + 3 + 2) + (2)$

\answerbox{61}

\input{08-06-06.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 7.

\SOLUTION

\input{08-06-07.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 8.

\SOLUTION

\input{08-06-08.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 9.

\SOLUTION

\input{08-06-09.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 10.
In how many ways can eight distinct balls be distributed
into three distinct urns if each urn must contain at least
one ball?

$3^8 - (C\binom{3}{1} \cdot 2^8) + (C\binom{3}{2} \cdot 1^8)$

\SOLUTION

\input{08-06-10.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 11.

\SOLUTION

????
%\input{08-06-11.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 12.

\SOLUTION

\input{08-06-12.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 13.

\SOLUTION

\input{08-06-13.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 14.

\SOLUTION

\input{08-06-14.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 15.

\SOLUTION

OMITTED SPRING2022
%\input{08-06-15.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 16.

\SOLUTION

\input{08-06-16.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 17.

(Show all work clearly.)

How many ways can the digits 0, 1, 2, 3, 4, 5, 6, 7, 8, 9 be
arranged so that no even digit is in its original position?

Digits {0,1,2,3,4,5,6,7,8,9} can be arranged 10! ways.

There are 5 even numbers in the list.

$10! - \binom{5}{1}9! + \binom{5}{2}8! - \binom{5}{3}7! + \binom{5}{4}6! -\binom{5}{5}5!$

$3628800-181440+403200-50400+3600-120$

\answerbox{2170680}

\SOLUTION

\input{08-06-17.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 22.

\SOLUTION

\input{08-06-22.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.6, question 23.

\SOLUTION

\input{08-06-23.tex}

%------------------------------------------------------------------------------
\newpage
\input{instructions.tex}
\end{document}
