\input{thispreamble.tex}

\renewcommand\AUTHOR{nweadick1@cougars.ccis.edu} % CHANGE TO YOURS

\begin{document}
\topmattertwo

\textsc{Objectives}
\begin{enumerate}
\item Compute recurrence relation.
\end{enumerate}
\vspace{1cm}



The following are practice problems for self-study:
\begin{enumerate}[nosep]
\li Rosen 8th edition, section 8.1: Odd numbered problems 1-31 except 15, 17,
23, 29.
\end{enumerate}
Some solutions are provided.
For this assignment the problems you need to solve are
\begin{enumerate}[nosep]
\li Rosen 8th edition, section 8.1: \underline{questions 4, 8, 12, 24}.
\end{enumerate}
Explain your work completely using the solutions provided as
guide and examples on how to write math properly.

In \LaTeX\, math notation is enclosed by the \verb!$! symbols.
For instance \verb!$x = a_{1} + b^{2}$! gives you $x = a_{1} + b^{2}$.
For emphasis you can write also write it as
\verb!\[ x = a_{1} + b^{2} \]!
to center your math:
\[
x = a_{1} + b^{2}
\]
For binomial coefficients, \verb!$\binom{5}{2}$! will give you 
$\binom{5}{2}$.
You can also look at the solutions, find something that you can use,
copy-and-paste, and modify.

For more information about \LaTeX\, go to my
website
\href{http://bit.ly/yliow0}{http://bit.ly/yliow0},
click on \verb!Yes!
you are one of my students,
then look for
\href{https://drive.google.com/file/d/0BzjYrK0VFuMWZm5xV0kyR3J2Zm8/view?usp=sharing}{latex.pdf}.)
Even easier: ask questions in CCCS discord.





Draw a box around your final answer if the question required
an explicit answer (i.e., if it's not a proof question).

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.1, question 1.

\SOLUTION

\input{08-01-01.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.1, question 2.

\SOLUTION

\input{08-01-02.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.1, question 3.

\SOLUTION

\input{08-01-03.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.1, question 4.
A country uses as currency coins with values of 1 peso,
2 pesos, 5 pesos, and 10 pesos and bills with values of
5 pesos, 10 pesos, 20 pesos, 50 pesos, and 100 pesos.
Find a recurrence relation for the number of ways to pay
a bill of n pesos if the order in which the coins and bills
are paid matters.

First 4 initial conditions

$a_1 = 1 , a_2 = 2, a_3 = 3, a_4 =5 $

if $a_n$ denotes the number of ways to deposit n pesos, we have the recurrence relation

for $n \geqslant 100$

$\{a_n = a_{n-1} + a_{n-2} + 2a_{n-5} + 2a_{n-10} 
+ a_{n-20} + a_{n-50} + a_{n-100}\}$

\SOLUTION

\input{08-01-04.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.1, question 8.
a) Find a recurrence relation for the number of bit strings
of length n that contain three consecutive 0s.
b) What are the initial conditions?
c) How many bit strings of length seven contain three
consecutive 0s?

(a) let $a_n$ be the number of bit strings of length n containing three consecutive 0s.

we have the recurrence relation

for $n \geqslant 3$

$\{a_n = a_{n-1} + a_{n-2} + a_{n-3} + 2^{n-3}\}$

\answerbox{$\{a_n = a_{n-1} + a_{n-2} + a_{n-3} + 2^{n-3}\}$}

(b) First 3 initial conditions are , 

\answerbox{$a_1 = 0, a_2 = 0, a_3 = 1$}

(c) 

$a_4 = 1 + 0 + 0 + 2^1 = 3$

$a_5 = 3 + 1 + 0 + 2^2 = 8$

$a_6 = 8 + 3 + 1 + 2^3 = 20$

$\{a_7 = a_{6} + a_{5} + a_{4} + 2^{4}\}$

$\{a_7 = 20 + 8 + 3 + 2^{4}\} = 47$

\answerbox{47}

\SOLUTION

\input{08-01-08.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.1, question 12.
a) Find a recurrence relation for the number of ways to
climb n stairs if the person climbing the stairs can take
one, two, or three stairs at a time.
b) What are the initial conditions?
c) In how many ways can this person climb a flight of
eight stairs?

(a)let $a_n$ be the number of ways to
climb n stairs if the person climbing the stairs can take
one, two, or three stairs at a time.

we have the recurrence relation

\answerbox{for $n \geqslant 3$ \{$a_n = a_{n-1} + a_{n-2} a_{n-3}$\}}

(b) The initial conditions are 

\answerbox{$a_0 = 1, a_1 = 1 , a_2 = 2, a_3 = 4$ }

(c) 

$a_4 = a_{3} + a_{2} + a_{1} = 4 + 2 + 1 = 7$

$a_5 = a_{4} + a_{3} + a_{2} = 7 + 4 + 2 = 13$

$a_6 = a_{5} + a_{4} + a_{3} = 13 + 7 + 4 = 24$

$a_7 = a_{6} + a_{5} + a_{4} = 24 + 13 + 7 = 44$

Now, $a_8 = a_{7} + a_{6} + a_{5} = 44 + 24 + 13 = 81$

\answerbox{81}


\SOLUTION

\input{08-01-12.tex}

%------------------------------------------------------------------------------
\newpage
\nextq Rosen 8th edition, section 8.1, question 24.
Find a recurrence relation for the number of bit sequences
of length n with an even number of 0s.

let $a_n $ be the number of bit sequences
of length n with an even number of 0s.

we have the recurrence relation

\answerbox{for $n \geqslant 2$ \{$a_n = a_{n-1} + 2^{n-1} - a_{n-1}$\}}

\SOLUTION

\input{08-01-24.tex}

%------------------------------------------------------------------------------
\newpage
\input{instructions.tex}
\end{document}
